---
title: "Project 3: project3package Tutorial"
author: Sabrina Yu & Yining Li
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project 3: PACKAGE_NAME Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(project3)
library(class)
library(palmerpenguins)
library(randomForest)
library(magrittr)
library(dplyr)
data(my_gapminder)
library(tibble)
library(ggplot2)
```

## 1. Introduction

This is the final project for STAT302. A package called "project3" is created, and it includes four functions: `my_t_test`, `my_lm`, `my_knn_cv`, and `my_rf_cv``.
package collaborators: Sabrina Yu & Yining Li
The guide to install the package:

```{r, eval = FALSE}
devtools::install_github("SabrinaYuY/project3", build_vignette = TRUE, build_opts = c())
library(project3)
# Use this to view the vignette in the Demo HTML help
help(package = "project3", help_type = "html")
# Use this to view the vignette as an isolated HTML file
utils::browseVignettes(package = "project3")
```
## 2. Tutorial for `my_t.test`

Use the `lifeExp` data from `my_gapminder` for the following tests

### Case I: alternative = "two.sided"
 \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &\neq 60.
  \end{align}
  
```{r}
# perform t-test with the alternative = two.sided
my_t.test(my_gapminder$lifeExp, mu = 60, alternative = "two.sided")
```
In this case, p-value is 0.093, which is greater than 0.05. Thus the result is not statistically significant.
We don't have enough evidence to reject the null hypothesis.

### Case II: alternative = "less"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &< 60.
  \end{align}
  
```{r}
# perform t-test with the alternative = less
my_t.test(my_gapminder$lifeExp, mu = 60, alternative = "less")
```
In this case, p-value is 0.047, which is less than 0.05. Thus the result is statistically significant.
We do have enough evidence to reject the null hypothesis. 

### case III: alternative = "greater"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &> 60.
  \end{align}
```{r}
# perform t-test with the alternative = greater
my_t.test(my_gapminder$lifeExp, mu = 60, alternative = "greater")
```
In this case, p-value is 0.0953, which is greater than 0.05. Thus the result is not statistically significant.
We don't have enough evidence to reject the null hypothesis.
